### 2023-04-12 definitions.tex
up
Starting

\begin{definition}
A {\em vector addition system with states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\N^d$-labeled directed graph $V = (Q,T)$, where $Q$ will be referred to as the {\em states} of $V$, and where $T \subseteq Q \times \N^d \times Q$ will be referred to as {\em transitions} of $V$. 
% The {\em size} of $V$ is defined as $|V|=|Q|+|T|*d*|log(||T||)$ where $||T||$ denotes the absolue value of the largest number that appears in $T$, i.e. $||T|| = max\{ ||\textbf{z}||: (p,\textbf{z},q) \in T\}$.
\end{definition}

Subsetquently, $Q \times \N^d$ denotes the set of configurations of $V$.
For every configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and every transition $t = (p, \textbf{z}, q)$ we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z}$.

@@

>>>>

\begin{definition}
A {\em vector addition system with states (VASS)} in dimension $d$ ($d$-VASS for short) is a finite $\mathds{Z}^d$-labeled directed graph $V = (Q,T)$, where $Q$ will be referred to as the {\em control states} of $V$, and where $T \subseteq Q \times \mathds{Z}^d \times Q$ will be referred to as {\em control transitions} of $V$. 
% The {\em size} of $V$ is defined as $|V|=|Q|+|T|*d*|log(||T||)$ where $||T||$ denotes the absolue value of the largest number that appears in $T$, i.e. $||T|| = max\{ ||\textbf{z}||: (p,\textbf{z},q) \in T\}$.
\end{definition}

Subsetquently, $Q \times \N^d$ denotes the set of configurations of $V$.
For every configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and every control transition $t = (p, \textbf{z}, q)$ we write $p(\textbf{u}) \xrightarrow{t} q(\textbf{v})$ whenever $\textbf{v} = \textbf{u} + \textbf{z}$.

@@

Op is the set of actions

% If $\gamma \in \{1, \ldots, d\}$, we write $\overline{\gamma}$ for the $\{1, \ldots, d\} \setminus \{\gamma\}$

\begin{definition}
A {\em reset VASS} in dimension $d$ ($d$-dim Reset VASS for short) is a finite 
% $\mathds{Z}^d$
labeled directed graph $V = (Q,T)$, where $Q$ will be referred to as the {\em control states} of $V$, and where 
%$T \subseteq Q \times \mathds{Z}^d \times Q$
$T \subseteq Q \times Op \times Q$
 will be referred to as {\em control transitions} of $V$. 
where $Op = \{ add(\textbf{z}) | \textbf{z} \in \mathds{Z}^d\} \cup 
		\{ reset(i) | i \in \{1,\ldots,d\} \}$.
\end{definition}

% $(Q, Op, \rightarrow)$

% $(S, Op, \rightarrow)$

Again $Q \times \N^d$
 denotes the set of configurations of $V$.
For every configurations $p(\textbf{u}), q(\textbf{v}) \in Q \times \N^d$ and every control transition

and the set of transitions is

\begin{itemize}

\item if $(q,\textbf{z},q') \in T_1$ then for all $\textbf{u} \in \N^d$ such that $\textbf{u}+\textbf{z} \geq 0$
 $q(\textbf{u}) \xrightarrow{\textbf{z}} q'(\textbf{u}+\textbf{z})$,

\item if $(q,\gamma,q') \in T_2$ then for all $\textbf{u} \in \N^d$ 
$q(\textbf{u}) \xrightarrow{z} q'(\textbf{u}')$,  where $\textbf{u}'[\gamma] = 0$ and $\textbf{u}'[\gamma'] = \textbf{u}[\gamma']$ for all $\gamma' \in \{1,\ldots, d\} \setminus \gamma$.

\end{itemize}
